\documentclass[12pt,a4paper]{article}

% ---------------- PACKAGES ----------------
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{float}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{longtable}
\usepackage{ragged2e}

% ---------------- COLORS ----------------
\definecolor{headerblue}{RGB}{52, 90, 150}
\definecolor{rowgray}{RGB}{240, 240, 245}
\definecolor{chosen}{RGB}{220, 240, 220}
\definecolor{badgered}{RGB}{220, 80, 60}
\definecolor{badgegreen}{RGB}{50, 150, 80}
\definecolor{badgeamber}{RGB}{200, 140, 20}
\definecolor{badgeblue}{RGB}{50, 110, 190}
\definecolor{lightred}{RGB}{255, 230, 225}
\definecolor{lightgreen}{RGB}{220, 245, 220}
\definecolor{lightamber}{RGB}{255, 248, 220}
\definecolor{lightblue}{RGB}{220, 235, 255}

% ---------------- CODE STYLE ----------------
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red},
    breaklines=true,
    frame=single
}

% ---------------- BADGE COMMAND ----------------
\newcommand{\badgegreen}[1]{%
  \colorbox{lightgreen}{\textcolor{badgegreen}{\footnotesize\textbf{#1}}}%
}
\newcommand{\badgered}[1]{%
  \colorbox{lightred}{\textcolor{badgered}{\footnotesize\textbf{#1}}}%
}
\newcommand{\badgeamber}[1]{%
  \colorbox{lightamber}{\textcolor{badgeamber}{\footnotesize\textbf{#1}}}%
}
\newcommand{\badgeblue}[1]{%
  \colorbox{lightblue}{\textcolor{badgeblue}{\footnotesize\textbf{#1}}}%
}

% ---------------- TITLE PAGE ----------------
\title{
    \vspace{2cm}
    \textbf{ Final Project Based Assignment: Automated Chemical Dosing System\\ 
    CS3243 IoT Devices and Applications } \\ 
    \vspace{4cm}
    \large Department of Computer Science and Engineering \\
    University of Moratuwa\\
    \vspace{1.5cm}
}

\author{
     Mudaliarachchi NS - 230415H  \\
    \vspace{1cm}
}

\date{\today}

% ---------------- DOCUMENT ----------------
\begin{document}

\maketitle

\newpage

% =========================================================
\section{Water Level Measurement Method }

Since the hospital prefers not to install any sensors inside the tank due to the periodic cleaning process, the possible way to install sensors is either on the top lid of the tank or externally at the discharge outlet point.

\subsection{Configurations of the Water Supply Tank}

\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Volume & 2000 Liters \\
Diameter & 50 cm \\
Height & 10.16 m \\
\hline
\end{tabular}
\caption{Water Supply Tank Specifications}
\end{table}

% =========================================================
\subsection{Method : Inferential Software Flow Integration Routine}

To satisfy the hospital's strict guidelines preventing any physical instrumentation from entering the 2000-liter purified water supply tank, a real-time Inferential Software Flow Integration Routine is deployed within the central controller.

This model tracks the exact volume of water entering and leaving the vessel by intercepting high-frequency square-wave pulse signals from two inline \href{https://www.duino.lk/product/ht30-water-flow-sensor-ac/}{SEN-HZ21WA miniature nylon Hall Effect turbine flow sensors} installed completely external to the tank housing.
\\ This product costs approximately \textbf{LKR 3000}.


\subsubsection*{Hardware Specifications}

\begin{table}[H]
\centering
\begin{tabular}{|p{5cm}|p{9cm}|}
\hline
\textbf{Hardware Parameter} & \textbf{Specification Value} \\
\hline
Model Number & SEN-HZ21WA Miniature Water Sensor \\
\hline
Material Construction & Nylon PA66 Polymer with Stainless Steel Impeller Shaft \\
\hline
Connection Profile & $1/2$ inch G-Thread / DN15 \\
\hline
Operational Flow Range & $1.0$ to $30.0$ L/min \\
\hline
Excitation Voltage Input & 5V DC \\
\hline
Sensor Mechanics & Magnetic impeller with isolated Hall Effect sensor \\
\hline
Signal Output Type & 5V square-wave digital pulse train \\
\hline
\end{tabular}
\caption{Flow Sensor Specifications}
\end{table}

Every $\Delta t = 1.0$ second, the controller samples the background registers and calculates the discrete fluid parameters.

The current net volume of water inside the tank is updated using the following discrete Riemann summation framework.

\[
V_{\text{current(new)}} =
V_{\text{current(old)}} + \Delta V_{\text{net}}
\]

\[
\Delta V_{\text{net}} =
(Q_{\text{in}} - Q_{\text{out}})\times \Delta t
\]

The instantaneous flow velocity parameters are derived in liters per minute.

\[
Q_{\text{in}} =
\left(
\frac{\text{Inflow Pulse Count}}
{\text{K-Factor}}
\right)\times 60
\]

\[
Q_{\text{out}} =
\left(
\frac{\text{Outflow Pulse Count}}
{\text{K-Factor}}
\right)\times 60
\]

The incremental volumetric deviation becomes:

\[
\Delta V_{\text{net}} =
\frac{\text{Inflow Pulses} - \text{Outflow Pulses}}
{450}
\]

This value is continuously added to the global storage variable to track active storage levels.

\subsubsection*{Converting Net Volume to Linear Height}

To drive the continuous digital readout gauge on the dashboard, the controller converts the running volume variable into a linear height profile.

Given the cylindrical geometric properties of the 2000L tank:

\[
r = 0.25m
\]

\[
A = \pi r^2
\]

\[
A = \pi(0.25)^2 \approx 0.19635m^2
\]

The real-time height profile is calculated as:

\[
V_{m^3} =
\frac{V_{\text{current}}}{1000}
\]

\[
H =
\frac{V_{m^3}}{A}
\]

This dynamic variable continuously updates the HMI graphical dashboard, allowing hospital maintenance crews to clean and manually scrub the internal tank structure without risking physical damage to instrumentation.

% =========================================================
\section{Concentrated Chemical Level Estimation Method}
To adhere to the strict constraint preventing the installation of level sensors inside the 10-liter concentrated chemical container, a highly reliable, non-intrusive Dual-Verification Framework is deployed.
% =========================================================
\subsection{Method: Dual-Verification (Mass-Computational) Level Tracking for Concentrated Chemical Estimation}

The system is configured around a standard 10-liter cylindrical or rectangular chemical supply vessel. The target fluid handled is industrial-grade Isopropyl Alcohol (IPA), which exhibits physical properties distinct from water.

\subsubsection*{Chemical Properties and Container Specifications}

\begin{itemize}
    \item \textbf{Fluid Density ($\rho_{\text{chem}}$):}  
    At room temperature ($27^\circ C$ - $32^\circ C$), the density of Isopropyl Alcohol is:
    
    \[
    \rho_{\text{chem}} = 785 \text{ kg/m}^3
    \]

    which is equivalent to:

    \[
    0.785 \text{ g/mL} = 0.785 \text{ kg/L}
    \]

    \item \textbf{Maximum Fluid Mass:}

    A completely full 10-liter chemical payload exerts a net liquid mass of:

    \[
    M_{\text{fluid}}
    =
    \text{Volume} \times \rho_{\text{chem}}
    \]

    \[
    M_{\text{fluid}}
    =
    10\text{ L} \times 0.785\text{ kg/L}
    =
    7.85\text{ kg}
    \]

    \item \textbf{Container Tare Weight:}

    The empty plastic chemical canister exhibits a static dead weight:

    \[
    M_{\text{tare}} \approx 0.35\text{ kg} - 0.50\text{ kg}
    \]

\end{itemize}

% =========================================================
\subsubsection*{1. Primary Physical Verification: External Load Cell Matrix}

An industrial strain-gauge load cell platform is installed directly beneath the canister assembly, isolating the electrical components entirely from chemical contact.

When a fresh container is positioned on the platform, the system filters out the weight of the platform frame and the container's dry plastic shell ($M_{\text{tare}}$).

The controller samples the raw live gross weight ($M_{\text{current}}$) and computes the true remaining physical volume ($V_{\text{mass}}$) via mass balance:

\[
V_{\text{mass}} (\text{Liters})
=
\frac{M_{\text{current}} - M_{\text{tare}}}
{\rho_{\text{chem}}}
\]

Because the fluid density is significantly lighter than water, this equation prevents a $21.5\%$ overestimation error that would occur if water-density constants were mistakenly applied to the software logic.

% =========================================================
\subsubsection*{2. Secondary Verification: Computational Flow Integration Model}

Operating in parallel with the weight sensor, an inferential software loop serves as a digital twin redundancy check.

As the chemical dosing pump draws fluid from the container, it passes through an inline micro-flow meter.

Because microcontrollers execute code within sequential loops at finite clock edges, the theoretical continuous integral for fluid displacement is represented as:

\[
V_{\text{dispensed}}
=
\int_{0}^{t} Q_{\text{chem}}(t)\,dt
\]

\[
\Delta t = 1.0\text{ second}
\]

The running algorithmic volume register updates dynamically every clock cycle:

\[
V_{\text{algorithm(new)}}
=
V_{\text{algorithm(old)}} - \Delta V
\]

\[
\Delta V
=
Q_{\text{chem}} \times \Delta t
\]

Where:

\begin{itemize}
    \item $Q_{\text{chem}}$ = Real-time volumetric flow rate extracted from the pulse frequency of the micro-flow meter ($\text{Liters/Second}$)

    \item $\Delta V$ = Absolute incremental volume drawn during the 1-second clock step ($\text{Liters}$)
\end{itemize}

% =========================================================
\newpage
\section{Hardware Specifications and Comparative Market Analysis}

This section presents a systematic evaluation of all hardware components required for the automated chemical dosing system. For each subsystem, three commercially available product options sourced from the Sri Lankan market and Foreign market are compared across cost, specifications, and suitability for the application. The recommended product for each category is highlighted in \colorbox{chosen}{green}.

% ---------------------------------------------------------
\subsection{Water Level Measurement - Inferential Flow Sensors}

The inferential software flow integration routine requires two inline Hall Effect turbine flow sensors installed externally on the inlet and outlet pipes of the 2000-liter water supply tank. This approach eliminates any physical instrumentation inside the tank, fully satisfying the hospital's strict cleaning protocol constraint. The total cost for two sensors is approximately \textbf{LKR 6,000}.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
\rowcolor{chosen}
SEN-HZ21WA (HT30) Hall Effect sensor &
\href{https://www.duino.lk/product/ht30-water-flow-sensor-ac/}{duino.lk} &
$\sim$LKR 3,000 &
1--30 L/min, 5V DC, 450 pulses/L, Nylon PA66 + stainless steel shaft, DN15 &
\badgegreen{Chosen} \\
\hline
G\textonehalf{} inch Hall sensor &
\href{https://www.duino.lk/product/g0-5-inch-water-flow-hall-sensor/}{duino.lk} &
$\sim$LKR 900 &
1--30 L/min, 5V DC, lower-cost plastic body &
\badgeamber{Budget alt.} \\
\hline
HT30 (AC-rated variant) &
\href{https://www.duino.lk/product/ht30-water-flow-sensor-ac/}{duino.lk} &
$\sim$LKR 3,000 &
Same model as chosen option; identical specifications &
\badgeblue{Duplicate} \\
\hline
\end{tabular}
\caption{Water Flow Sensor Comparison (Inferential Level Method)}
\end{table}

\noindent\textbf{Justification:} The SEN-HZ21WA is selected for its stainless steel impeller shaft, which provides superior corrosion resistance compared to fully plastic alternatives. At LKR 3,000 per unit, it is significantly cheaper than the commented-out ultrasonic option (LKR 65,500) and the industrial load cell option (LKR 17,479), while fully meeting the no-sensor-inside-tank constraint.

% ---------------------------------------------------------
\subsection{Chemical Level Estimation - Load Cell}

The dual-verification framework uses a strain-gauge load cell platform mounted beneath the 10-liter IPA canister. The maximum payload is approximately 8.35 kg (7.85 kg fluid + 0.50 kg container). The load cell must accommodate this weight with adequate safety margin.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
CZL-601 60 kg S-type load cell &
\href{https://tronic.lk/product/czl-601-load-cell-60kg-130x30x22mm}{tronic.lk} &
$\sim$LKR 2,500 &
60 kg capacity, S-type aluminium, HX711 compatible &
\badgegreen{Suitable} \\
\hline
20 kg load cell &
\href{https://www.duino.lk/product/20kg-load-cell-weighing-sensor/}{duino.lk} &
$\sim$LKR 1,200 &
20 kg max marginal for 8.35 kg payload; minimal overload margin &
\badgered{Risky} \\
\hline
\rowcolor{chosen}
50 kg body load cell &
\href{https://www.duino.lk/product/50kg-body-load-cell/}{duino.lk} &
$\sim$LKR 1,800 &
50 kg max, ample overload headroom, HX711 compatible &
\badgegreen{Best fit} \\
\hline
\end{tabular}
\caption{Load Cell Comparison (Chemical Canister Weighing)}
\end{table}

\noindent\textbf{Justification:} The 50 kg load cell provides a 6$\times$ safety margin over the maximum payload of 8.35 kg, ensuring reliable operation without risk of overload. The 20 kg option is technically borderline and unsuitable for a hospital environment where reliability is critical. The 60 kg CZL-601 functions correctly but reduces measurement resolution since the active range (0--8.35 kg) is a smaller fraction of its full scale.

% ---------------------------------------------------------
\subsection{Dispensing Tank Level Sensors}

Each 750 mL dispensing tank requires a single low-level binary sensor to detect when the chemical level falls below the refill threshold. The sensor is fitted externally to avoid chemical contact, and only on/off detection is required — continuous level measurement is not needed for this subsystem.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
\rowcolor{chosen}
JSN-SR04T waterproof ultrasonic sensor &
\href{https://lk-tronics.com/product/jsn-sr04-waterproof-ultrasonic-distance-measuring-transducer-sensors/}{lk-tronics.com} &
$\sim$LKR 950 &
IP67 rated, 20--450 cm range, chemical-splash resistant, sealed probe &
\badgegreen{BestFit} \\
\hline
HC-SR04 standard ultrasonic &
\href{https://tronic.lk/product/hc-sr04-4pin-ultrasonic-sensor-module}{tronic.lk} &
$\sim$LKR 350 &
2--400 cm range, NOT waterproof, exposed PCB — chemical exposure risk &
\badgered{Not Suitable} \\
\hline
DFRobot gravity liquid sensor &
\href{https://www.dfrobot.com/product-2059.html}{dfrobot.com} &
$\sim$LKR 58, 000 &
Non-contact through-wall capacitive detection, corrosion-proof, fully sealed &
\badgeblue{Budget alt.} \\
\hline
\end{tabular}
\caption{Dispensing Tank Level Sensor Comparison}
\end{table}

\noindent\textbf{Justification:} The JSN-SR04T is the optimal choice. Its IP67 waterproof rating protects against chemical splashes in the dispensing environment, unlike the bare HC-SR04. The DFRobot capacitive sensor offers superior non-contact through-wall sensing and is the preferred option if the dispensing tanks are sealed plastic containers, at a higher cost premium.

% ---------------------------------------------------------
\subsection{Flow Meters - Chemical Dosing Line}

The chemical dosing pump flow rate is controlled via a PWM signal but does not guarantee accurate flow. An inline flow meter on the chemical line measures the actual dispensed volume in real time, forming the secondary verification channel of the dual-verification framework.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
YF-S201 Hall effect flow sensor &
\href{https://lk-tronics.com/product/yf-s201-water-flow-sensor/}{lk-tronics.com} &
$\sim$LKR 650 &
1--30 L/min, 5V, Hall pulse output, ABS plastic body &
\badgeamber{Check IPA compat.} \\
\hline
Magnetic plastic flow sensor &
\href{https://www.duino.lk/product/magnetic-plastic-water-flow-sensor/}{duino.lk} &
$\sim$LKR 600 &
Low flow range, food-grade plastic body &
\badgeamber{Verify compat.} \\
\hline
\rowcolor{chosen}
YF-S201C G\textonehalf{} Hall effect sensor &
\href{https://www.duino.lk/product/yf-s201c-g1-2-hall-effect-liquid-water-flow-sensor/}{duino.lk} &
$\sim$LKR 700 &
G\textonehalf{} thread fitting, Hall pulse output, slightly more robust pipe connection &
\badgegreen{Good fit} \\
\hline
\end{tabular}
\caption{Chemical Line Flow Meter Comparison}
\end{table}

\noindent\textbf{Important Note:} IPA (Isopropyl Alcohol) can degrade standard NBR rubber O-rings and ABS seals over time. Before finalising any flow sensor for the chemical line, the impeller shaft material, O-ring compound, and housing material must be verified for IPA compatibility. PTFE or Viton-lined sensors are the recommended alternative for long-term deployments.

% ---------------------------------------------------------
\subsection{Control Valves - Dispensing Tank Inlets}

Each dispensing tank requires a solenoid-controlled valve to regulate chemical inflow. The system may serve tens of dispensing tanks distributed throughout the hospital premises, making per-unit cost a significant factor.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
Tuya Zigbee smart gas valve &
\href{https://www.daraz.lk}{daraz.lk} &
$\sim$LKR 7,769 &
Zigbee wireless, smart-home integration, timer function, \textonehalf--1 inch &
\badgered{Overkill / costly} \\
\hline
\rowcolor{chosen}
FPD270A \textonehalf{} inch solenoid valve (220V) &
\href{https://www.duino.lk/product/fpd270a-1-2-220v-electric-solenoid-valve/}{duino.lk} &
$\sim$LKR 900 &
220V AC, \textonehalf{} inch, normally closed, direct relay control from MCU &
\badgegreen{Best value} \\
\hline
4\,mm pneumatic flow control valve &
\href{https://www.duino.lk/product/4mm-pneumatic-air-flow-control-valve/}{duino.lk} &
$\sim$LKR 300 &
Pneumatic, 4\,mm tube fitting — designed for air/gas, not liquid pipelines &
\badgered{Wrong type} \\
\hline
\end{tabular}
\caption{Control Valve Comparison (Dispensing Tank Inlets)}
\end{table}

\noindent\textbf{Justification:} With potentially tens of dispensing tanks, the FPD270A at LKR 900 per valve is the clear choice. It is driven through a relay module directly from the MCU, requires no wireless protocol stack, and is purpose-built for liquid pipelines. The Tuya Zigbee valve is designed for smart-home irrigation and gas shutoff applications and would add unnecessary cost and protocol complexity to the IoT architecture.

% ---------------------------------------------------------
\subsection{Variable Rate Pump - Chemical Dosing}

The chemical dosing pump must deliver IPA at a controllable flow rate via PWM, with the actual flow measured by the inline flow meter. Since IPA is a chemical solvent, fluid compatibility with the pump internals is the primary selection criterion.

\vspace{0.3cm}
\noindent\textbf{Comparative Analysis:}

\begin{table}[H]
\centering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{3.2cm}|p{3.5cm}|p{2.2cm}|p{3.5cm}|p{2cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Product}} &
\textcolor{white}{\textbf{Supplier}} &
\textcolor{white}{\textbf{Est. Cost}} &
\textcolor{white}{\textbf{Key Specifications}} &
\textcolor{white}{\textbf{Verdict}} \\
\hline
100\,W submersible water pump &
\href{https://www.duino.lk/product/100w-submersible-water-pump-4-5m/}{duino.lk} &
$\sim$LKR 3,500 &
PWM-controllable, 4.5\,m head — designed for water, chemical compatibility unverified &
\badgered{$\triangle$ Compat. risk} \\
\hline
\rowcolor{chosen}
Peristaltic liquid dosing pump &
\href{https://www.duino.lk/product/peristaltic-liquid-pump-dosing-pump/}{duino.lk} &
$\sim$LKR 2,800 &
Fluid isolated inside silicone/rubber tube; pump body never contacts IPA; PWM speed control &
\badgegreen{Best for chemicals} \\
\hline
220V 1000\,L/h submersible pump &
\href{https://www.duino.lk/product/220v-25w-1000l-h-1-8m-submersible-water-pump-for-fish-tank-fountains-hydroponics-ponds-aquariums/}{duino.lk} &
$\sim$LKR 1,800 &
1000\,L/h flow rate — far exceeds dosing requirement for 750\,mL dispensing tanks &
\badgered{Flow rate too high} \\
\hline
\end{tabular}
\caption{Chemical Dosing Pump Comparison}
\end{table}

\noindent\textbf{Justification:} The peristaltic dosing pump is the architecturally correct choice for this application. In a peristaltic design, the pumped fluid travels entirely inside a replaceable tube, meaning the IPA never contacts the pump motor, housing, or impeller assembly. This eliminates chemical compatibility concerns entirely. PWM speed control is also more linear for peristaltic pumps than centrifugal designs, improving dosing accuracy.

% ---------------------------------------------------------
\subsection{Summary Cost Comparison}

Table~\ref{tab:cost_summary} consolidates the recommended products and their estimated unit costs.

\begin{table}[H]
\centering
\setlength{\tabcolsep}{6pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{|p{4cm}|p{4.5cm}|p{2cm}|p{2.5cm}|}
\hline
\rowcolor{headerblue}
\textcolor{white}{\textbf{Subsystem}} &
\textcolor{white}{\textbf{Selected Product}} &
\textcolor{white}{\textbf{Unit Cost (LKR)}} &
\textcolor{white}{\textbf{Qty (min.)}} \\
\hline
\rowcolor{rowgray}
Water level — flow sensor & SEN-HZ21WA (HT30) & $\sim$3,000 & 2 \\
\hline
Chemical level — load cell & 50\,kg body load cell & $\sim$1,800 & 1 \\
\hline
\rowcolor{rowgray}
Dispensing tank sensor & JSN-SR04T ultrasonic & $\sim$950 & $n$ tanks \\
\hline
Chemical line flow meter & YF-S201C G\textonehalf{} & $\sim$700 & 1 \\
\hline
\rowcolor{rowgray}
Control valve (per tank) & FPD270A solenoid & $\sim$900 & $n$ tanks \\
\hline
Dosing pump & Peristaltic pump & $\sim$2,800 & 1 \\
\hline
\end{tabular}
\caption{Recommended Component Cost Summary}
\label{tab:cost_summary}
\end{table}

\noindent The minimum fixed hardware cost (excluding dispensing-tank-count-dependent components) is approximately \textbf{LKR 14,300}. Each additional dispensing tank requires one JSN-SR04T sensor ($\sim$LKR 950) and one FPD270A solenoid valve ($\sim$LKR 900), totalling \textbf{LKR 1,850 per tank}.

\end{document}